Honey bees vary collective decision making in different landscapes

### 2022-08-02 README.Rmd
inital commit to store as feature branch
tidied up analysis code and moved reference to the paper into inst

The goal of wagglefit is to allow for easy waggle dance analysis.

@@

You can install the released version of wagglefit from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wagglefit")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joseph-palmer/wagglefit")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wagglefit)
## basic example code
```

>>>>

wagglefit is an R package to analyse waggle run distributions and estimate the resulting proportions of scout and recruit dances, providing an estimate of dance use in undisturbed colonies.

@@

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("joseph-palmer/wagglefit")
```

when citing wagglefit please use (insert citation for publication).

## Honey bees vary collective decision making in different landscapes

All code used in the publication (insert citation link) is stored in `inst/publication/`.

## Reporting issues

If you notice any issues with this code please raise an issue in the github repo.

### 2022-08-02 inst/publication/Code/agent_based_sim.Rmd
tidied up analysis code and moved reference to the paper into inst

The code for the honeybee foraging simulation is writen in python and is contained in the `Simulation` directory (specifically `Simulation/Code`). The results of the simulation (as output csv files) are stored in `Results/Results`. Generating the results can be done by running the script `run.py` in `Simulation/Code`. Once you have ran the simulation you can run through this Rmd doc to generate the figures. To run the python code you will need python 3 installed.

@@

# load data
recruit <- read.csv(
  "Simulation/Results/recruit_distribution_v2.csv",
  header = FALSE
)
scout <- read.csv(
  "Simulation/Results/scout_distribution_v2.csv",
  header = FALSE
)

@@

ggsave(
  plot = combplot,
  filename = "Simulation/Results/combined_fit.png",
  width = 70.1,
  height = 81.79,
  units = "mm",
  dpi = 400
)
```
From this analysis we observe that the distribution of foraging distances reported by scouts is better described by an exponential than the minimum of an exponential, whereas the converse is true for foraging distances reported by reruits. These results support our hypothesis for how scout and recruit reported foraging distances occur through different processes and produce different patterns.

>>>>

The code for the honeybee foraging simulation is written in python and is contained in the `Simulation` directory (specifically `Simulation/Code`). The results of the simulation (as output csv files) are stored in `Results/`. Generating the results can be done by running the script `run.py` in `Simulation/Code`. Once you have ran the simulation you can run through this Rmd doc to generate the figures. To run the python code you will need python 3 installed along with the required packages.

@@

# load data
recruit <- read.csv(
  "Simulation/Results/recruit_distribution.csv",
  header = FALSE
)
scout <- read.csv(
  "Simulation/Results/scout_distribution.csv",
  header = FALSE
)

@@

ggsave(
  plot = combplot,
  filename = "Simulation/Results/combined_fit.png",
  width = 70.1,
  height = 81.79,
  units = "mm",
  dpi = 400
)
```
From this analysis we observe that the distribution of foraging distances reported by scouts is better described by an exponential than the minimum of an exponential, whereas the converse is true for foraging distances reported by recruits. These results support our hypothesis for how scout and recruit reported foraging distances occur through different processes and produce different patterns.

### 2022-08-02 inst/publication/Manuscript/paper.Rmd
tidied up analysis code and moved reference to the paper into inst

---
title: "Honeybees vary collective decision making in different landscapes. "
# author: "Joseph Palmer, Ash Samuelson, Rich Gill, Elli Leadbeater and Vincent A. A. Jansen"
output:
  word_document
always_allow_html: true
bibliography: reffs.bib
csl: science.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(showtext)
showtext_auto()

>>>>

---
title: "Honey bees vary collective decision making in different landscapes"
# author: "Joseph Palmer, Ash Samuelson, Rich Gill, Elli Leadbeater and Vincent A. A. Jansen"
output:
  word_document
always_allow_html: true
bibliography: reffs.bib
csl: science.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(showtext)
showtext_auto()
